On the presentation of orthogonal groups over polynomial rings

### 2019-05-27 dl-paper.tex
Added Proposition 5

\begin{corollary} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$.
Consequently one has \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]\end{corollary} \begin{proof}
Fix an element $g \in P_\alpha(m)$ and write it $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$.
Now by~\eqref{eq:Smult} and~\cref{P0_conj} one has
\begin{multline} \nonumber S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am) = 
\\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle \in P_\alpha\left(\tfrac{m}{1+am}\right). \end{multline}

@@

The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a partial function $t_\alpha(aX^{-1}) \colon V \not\to V$.
This function is defined for those triples $(g, h, u)$ for which $p(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
If $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$, then $t_\alpha(aX^{-1})$ is given by the following identity:
\[ t_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right).\]
It is easy to verify that $p(t_\alpha(aX^{-1}) (g, h, u)) = S_\alpha(a, p(g, h, u)).$

\begin{lemma} Let $\Phi$ be a simply-laced root system of rank $\geq 3$ and $(A, M)$ be a local pair. Then for $\alpha \in \Phi$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ descends to a well-defined total function 
  $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
\begin{proof}
 First of all, let us show that the resulting function is total. 
 Fix $(g, h, u) \in V$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
 Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
 $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
  which shows that $t_\alpha(aX^{-1})$ is defined on $(g, h \cdot i_+(h_0), u)$, which is also a representative of the same orbit as $(g, h, u)$.

@@

The next step of the proof is to pass from the set $V_0'$ to its quotient $V_0$ 
We allow multiplying the second component on the right by an element of $\mathrm{im}(\St(\Phi, A, M) \to \St(\Phi, A))$
 (this operation is well defined for $V'_0$).

\begin{multline}
 T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
 = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right),\text{ since} \end{multline} 
 \begin{multline}
h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-\tfrac{bX^{-1}}{1 + \tfrac{bm}{1+am}}\right) = \\ = 
 h \cdot x_\alpha\left(- \tfrac{aX^{-1}}{1 + am} - \tfrac{bX^{-1}}{(1+am)(1 + am + bm)}\right) \cdot h^{-1}_\alpha(1+am) \sim  
  h \cdot x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + am + bm}\right).
\end{multline}

>>>>

\begin{corollary}\label{SR:additivity} For $g \in P_\alpha(m)$ holds $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \tfrac{m}{1 + am})$.
Consequently one has \[ S_\alpha(a+b, g) = S_\alpha\left(b,\ S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am)\right)\cdot h_\alpha(1+am). \]\end{corollary} \begin{proof}
Fix an element $g \in P_\alpha(m)$ and write it $g = g_0 \cdot x_{-\alpha}(mX)$ for some $g_0 \in P_\alpha(0)$.
Now by~\eqref{eq:Smult} and~\cref{P0_conj} one has
\begin{multline} \nonumber S_\alpha(a, g) \cdot h_{\alpha}^{-1}(1+am) = S_\alpha(a, g_0) \cdot S_\alpha(a, x_{-\alpha}(mX)) \cdot h_{\alpha}^{-1}(1+am) = 
\\ = S_\alpha(a, g_0) \cdot x_{-\alpha}\left(\tfrac{mX}{1+am}\right) \cdot\langle a, m \rangle \in P_\alpha\left(\tfrac{m}{1+am}\right). \end{multline}

@@

The next step of the proof is to define for $\alpha \in \Phi$, $a \in A$ a partial function $t_\alpha(aX^{-1}) \colon V \not\to V$.
This function is defined for those triples $(g, h, u)$ for which $p(g, h, u) \in P_\alpha(*) \subseteq \overline{G}_M^{\geq 0}$.
If $p(g, h, u)$ happens to belong to $P_\alpha(m)$ for some $m \in M$, then $t_\alpha(aX^{-1})$ is given by the following identity:
\[ t_\alpha(aX^{-1}) (g, h, u) = \left( x_\alpha(aX^{-1})\cdot g ,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right),\ u \cdot (1 + am)\right).\]

From~\cref{SR:additivity} it follows that
\[p\left(t_\alpha(aX^{-1}) (g, h, u)\right) = S_\alpha(a, p(g, h, u)) \in P_\alpha(*) \cdot h_{\alpha}^{-1}(1+am) \subseteq G_M^{\geq 0},\]
therefore the operation $t_\alpha(aX^{-1})$ is well-defined.

\begin{lemma}\label{lem:orbit-action} Let $\Phi$ be a simply-laced root system of rank $\geq 3$ and $(A, M)$ be a local pair. 
Then for any $\alpha \in \Phi$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ gives rise to a well-defined total orbit function $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
\begin{proof}
 First of all, let us show that the resulting function is total. 
 Fix $(g, h, u) \in V$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
 Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
 $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
  which shows that $t_\alpha(aX^{-1})$ is defined on $(g, h \cdot i_+(h_0), u)$, which is also a representative of the same orbit as $(g, h, u)$.

@@

\begin{prop}
 The operators $T_\alpha(aX^{-1})$ satisfy relations $\text{R1}_1, $ $\text{R2}_1$.
\end{prop}
\begin{proof}
Suppose $(g, h, u)$ is such that $p(g, h, u) \in P_\alpha(m)$ for some $m \in M$.
Set $h' := x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-bX^{-1}\left(1 + \tfrac{bm}{1+am}\right)^{-1}\right) =
  x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + (a + b)m}\right) \cdot h^{-1}_\alpha(1+am).$
Invoking~\cref{SR:additivity} once again we obtain that
\begin{multline} \nonumber t_\alpha(bX^{-1}) t_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
t_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
 = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h \cdot h',\ u(1 + am + bm) \right) \sim t_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right), \end{multline} 
which implies the assertion for $\text{R1}_1$.

Now let us verify $\text{R2}_1$. Let $\alpha, \beta$ be a pair of roots such that $\alpha + \beta \in \Phi$. 
Notice that we could assume from the start that $p(g, h, u) \in j_+(K(A[X], M[X]) \cap P_\alpha(m) \cap P_{\alpha + \beta}(m'))$ for some $m,m' \in M$ (cf. the first part of the proof of~\cref{lem:orbit-action}). Now for $a, b \in A$ set $\epsilon = N_{?, ?}$ and $c = 1 + \epsilon abm'$.
It is clear that $\alpha$ and $\alpha+\beta$ form a sharp angle.
\begin{multline} \nonumber
[T_\alpha(a), T_\beta(bX^{-1})] \left( g, h, u \right) =
 T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) \cdot g, h \cdot x_\beta\left(\tfrac{bX^{-1}}{1-bm}\right) , u (1 - bm) \right) \sim \\
 \sim T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) g, h \cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')), u (1 - bm) \right) = \\
 = \left([x_\alpha(a), x_\beta(bX^{-1})] g, h', u (1 + abm')\right) \sim T_{\alpha}(N_{\alpha, \beta}abX^{-1})(g, h, u), \text{ since}\end{multline} 
 \begin{multline} \nonumber
 h' = h\cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm'))\cdot x_\beta\left(-\tfrac{b(1 - bm)X^{-1}}{1 + abm'}\right) \sim \\ \sim  h\cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha + \beta}\left(-N_{\alpha, \beta}\cdot ab(1-bm)X^{-1}\right)\cdot x_\beta\left(-\tfrac{b(1 - bm)X^{-1}}{1 + abm'}\right) = \\
 = h\cdot x_\beta\left(\tfrac{b X^{-1}}{1-bm}\right) \cdot x_{\alpha + \beta}\left(-\tfrac{N_{\alpha, \beta} \cdot abX^{-1}}{1-abm'}\right)\cdot x_\beta\left(-\tfrac{bX^{-1}}{1 - bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm') \sim
 h\cdot x_{\alpha + \beta}\left(\tfrac{N_{\alpha, \beta} \cdot abX^{-1}}{1+abm'}\right).
\end{multline}
\end{proof}
